Global Deaths Due to Air Pollution

### 2022-05-02 outline.Rmd
more updates

@@

Here's a graph to clearly visualize the previous table
```{r, echo=FALSE, message=FALSE}
#Plot High Population Deaths (average)
h<- ggplot(deaths_highpop_countries)+
  geom_col(mapping = aes(x=country, y=average_death_high))+
             xlab("Country")+
             ylab("Average deaths (per 100,000)")+
             ggtitle("Average total deaths in high-population countries")+
  coord_flip()

@@

#Plot of Low Population Deaths (average)
l <- ggplot(deaths_lowpop_countries)+
  geom_col(mapping = aes(x=country, y=average_death_low))+
             xlab("Country")+
             ylab("Average deaths (per 100,000)")+
             ggtitle("Average total deaths in low-population countries")+
  coord_flip()

@@

#Mean total deaths from 1990-2017 of high-population countries
deaths_lowpop_countries<- deaths_df %>% 
  filter(year> 1995 & country %in% c('Canada', 'Chile', 'Malawi', 'Serbia', 'Sri Lanka', 'New Zealand')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_low = mean(total_deaths))

#death_lowpop_countries
kable(list(deaths_highpop_countries, deaths_lowpop_countries))

>>>>

```{r, echo=FALSE}
ggplot(data=joined_high, aes(x=year, y=Count, color=country, size = total_deaths/Count)) +
  geom_line() +
  labs(title="Percentage of Death Count High Population", subtitle="Bar width is equal to percentage of Deaths")+
  xlab("Year")+
  ylab("Population")

ggplot(data=joined_low, aes(x=year, y=Count, color=country, size = total_deaths/Count)) +
  geom_line() +
  labs(title="Percentage of Death Count Low Population", subtitle="Bar width is equal to percentage of Deaths")+
  xlab("Year")+
  ylab("Population")
```

@@

Here's a graph to clearly visualize the previous table
```{r, echo=FALSE, message=FALSE}
#Plot High Population Deaths (average)
h<- ggplot(deaths_highpop_countries)+
  geom_col(mapping = aes(x=country, y=average_death_high, color=country))+
             xlab("Country")+
             ylab("Average deaths (per 100,000)")+
             ggtitle("Average total deaths in high-population countries")+
  coord_flip()

@@

#Plot of Low Population Deaths (average)
l <- ggplot(deaths_lowpop_countries)+
  geom_col(mapping = aes(x=country, y=average_death_low, color=country))+
             xlab("Country")+
             ylab("Average deaths (per 100,000)")+
             ggtitle("Average total deaths in low-population countries")+
  coord_flip()

@@

#Mean total deaths from 1990-2017 of high-population countries
deaths_lowpop_countries<- deaths_df %>% 
  filter(country %in% c('Canada', 'Chile', 'Malawi', 'Serbia', 'Sri Lanka', 'New Zealand')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_low = mean(total_deaths))

#Average Death of both High and Low Populated countries  
kable(list(deaths_highpop_countries, deaths_lowpop_countries))
